GSS Education Analysis (Working Title)

### 2023-03-12 outputs/paper/paper.qmd
add graphs

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = degree, fill = class)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "Highest Level of Education",
       x = "Number",
       fill = "Self-Ascribed Class")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

>>>>

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = degree, fill = class)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "Highest Level of Education",
       x = "Number",
       fill = "Self-Ascribed Class")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```
```{r}
#| echo: false
#| warning: false
#| label: fig-9
#| fig-cap: "rich work vs class"

#### Creating Graph ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(x = richwork, fill = class)) +
  geom_bar() + 
  theme_classic() +
  labs(x = "richwork",
       y = "number",
       fill = "class")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-10
#| fig-cap: "richwork vs satfin"

#### Creating Graph to  ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(x = richwork, fill = satfin)) +
  geom_bar() + 
  theme_classic() +
  labs(x = "richwork",
       y = "number",
       fill = "satfin")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-11
#| fig-cap: "richwork vs finrela"

#### Creating Graph to  ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(x = richwork, fill = finrela)) +
  geom_bar() + 
  theme_classic() +
  labs(x = "richwork",
       y = "number",
       fill = "finrela")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-12
#| fig-cap: "satfin vs satjob"

#### Creating Graph to  ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = satfin, fill = satjob)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "satfin",
       x = "number",
       fill = "satjob")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-13
#| fig-cap: "satfin vs class"

#### Creating Graph to  ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = satfin, fill = class)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "satfin",
       x = "number",
       fill = "class")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-14
#| fig-cap: "satfin vs finrela"

#### Creating Graph to  ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = satfin, fill = finrela)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "satfin",
       x = "number",
       fill = "finrela")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-15
#| fig-cap: "satfin vs degree"

#### Creating Graph to  ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = satfin, fill = degree)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "satfin",
       x = "number",
       fill = "degree")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-16
#| fig-cap: "finrela vs class"

#### Creating Graph to  ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = finrela, fill = class)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "finrela",
       x = "number",
       fill = "class")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-17
#| fig-cap: "finrela vs satjob"

#### Creating Graph to  ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = finrela, fill = satjob)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "finrela",
       x = "number",
       fill = "satjob")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-18
#| fig-cap: "finrela vs satjob"

#### Creating Graph to  ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = finrela, fill = satfin)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "finrela",
       x = "number",
       fill = "satfin")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```
